\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{listings}
%for dotex
\usepackage[pdftex]{graphicx}
\usepackage[pdf]{graphviz}
\usepackage[boxed]{algorithm2e} %end for dote
\usepackage{color}

\title{Isaac Doesn't Bless Jacob}
\begin{document}
\maketitle
\section{The Problem}

We need to authenticate users across various systems, both internal and external.
Isaac is a service that validates JWTs based on our user database, while
still avoiding sessions.

The use cases this service is designed to address are.
\begin{enumerate}
    \item Validate token signatures.
    \item Invalidate tokens for non existent or banned users.
    \item Invalidate tokens from valid users that were compromised. 
\end{enumerate}

\section{Use Cases}
\subsection{Validate Token Signatures}

The primary purpose of this service is to identify good tokens from bad. The first
line of defense against forged tokens is validating the JWT signature.

A JWT is composed of three parts, the header, payload, and signature.
We are using RS256 signing algorithm which uses asymmetric RSA keys. The JWT
is signed with the private key and validated with the public key.

Since we are only supporting RS256, the implementation is straight forward and
simpler. Simpler is better when it comes to security. Restricting the signing 
algorithm will prevent attacks such as forging a JWT using HMAC and using
the public key as the secret.

\subsection{Invalidate Tokens for Non Existent or Banned Users}

JWTs art designed to be stateless. Meaning that the server does not store any 
session information and the client has the sole responsibility of remembering the
token. However, the only feature of invalidating a JWT is an expiration date. 

We want to support invalidating tokens based on banning and removing users so
we can protect our client's data. This is why the service will check the user 
database to validate whether the user is active and able to have access to the system.

\subsection{Invalidate Tokens from Valid Users That Were Compromised}

Another challenge is how to invalidate JWTs from a valid user but their
token's were compromised some way. Each user will have something called a "ratchet"
which is an integer that can increment to invalidate old tokens.

The service will check and make sure the JWT's ratchet number matches that of
the user in the database.

\section{Design}

\subsection{Overview}

The two biggest features the service must have are safety and performance.

Safety because all requests to private routes need to be authenticated. We want
to maintain JWT's sessionless design while still retaining the ability to invalidate
tokens.

Performance because all requests to internal systems will require validation.
The service will have to handle a high load.

To maintain performance, we will utilize a cache to limit DB access and to 
maintain safety, we will use "green river" to prevent a stale cache.

\digraph[scale=0.80]{IsaacDesign}{
    splines="ortho";
    rankdir=TD;
    node [shape=box,style=filled,fillcolor="lightblue"];

    subgraph zero{
        rank=same;
        Client [shape=egg]
    };
    subgraph first{
        rank=same;
        query [shape=rectangle,label="Query Service"];
        cache [shape=signature,label="User Cache Service"];
    };
    subgraph second {
        rank=same;
        DB [shape=box3d];
        green [shape=rectangle,label="Green River"];
    };

    Client -> query;
    query -> Client;
    query -> cache;
    query -> DB 
    DB -> green;
    green -> cache;
}

\subsection{Safety and Performance}

Safety and performance are forces that are constantly pulling on each other.
The main feature for performance in this services is a cache so that the service
can minimize DB access. The problem with maintaining a cache is obviously that
the data goes stale. 

For security, we need to be able to invalidate the cache for a user/token as 
soon as the DB data changes.

Fortunately one foundational feature of the FoxCommerce system is the event sourcing
model. All changes to the DB are handles by "green river" workers. We can then
utilize this system to invalidate the cache in the auth service as soon as data
in the DB changes.

This means we can invalidate JWTs with little latency to maintain safety and 
prevent a stale cache.

\end{document}
